\documentclass[10pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[english]{babel}

\usepackage{enumitem}
\setlist{nosep}

\usepackage{resume}


\begin{document}
\sloppy


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent{\LARGE \textbf{Jan Nelson}}
\sbull jn123456789@gmail.com
\sbull https://github.com/jn123456789


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\spacedhrule{0.8em}{-0.4em}

\roottitle{About Me}

\noindent I am a seasoned veteran of the industry with a versatile skill set and a drive to
always be learning more. I have a passion for tackling hard problems head-on and rooting out
complexity wherever it resides. Whether adding a feature, tracking a bug, deploying
infrastructure, or hammering out process with my colleagues, my focus is on developing a
complete and sustainable solution to the challenge before me.  I believe in the power of the
team over the individual, and strive always to share knowledge and strengthen collaboration with
my fellows. I have two goals in my professional life:\ to build excellent software systems, and
to help everyone around me to be as excellent as they can possibly be.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\spacedhrule{0.8em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\textbf{Software Engineer} at Minerva Project}
  {Apr 2015 -- Present}
  {\\The Minerva Project is a university with a radical new approach to teaching that makes
    heavy use of web technology, both in teaching classes using the video conferencing
    environment known as the Active Learning Forum (ALF), and in its admissions process. My
    major contributions include the following:
   \begin{itemize}
   \item A distributed web service for recording classes conducted on the ALF. A master process
     (written in Node.js) communicates with clients via HTTP and launches EC2 instances to host
     worker processes that fulfill client requests.  Worker processes (also written in Node.js)
     communicate with the master process via Amazon SQS, coordinate selenium, chromedriver,
     xvfb, and ffmpeg subprocesses to connect to the class and record it, then compress the
     resulting video and upload it to S3. The service has been used to record over 2,000 classes
     to date with a greater than 99\% success rate.
   \item A Django/React application used by our faculty to review and grade the students'
     participation in class based on the aforementioned recordings. The application allows a
     user to play back the video from the class, jump around to parts where a particular student
     was heard speaking, enter grades for their participation, and write feedback comments for
     students to read.
   \item A Django/React application used by our admissions staff to evaluate videos submitted by
     prospective students. The application plays the video recorded by the student, and presents
     to the reviewer a decision tree in the form of a series of multiple-choice questions. The
     reviewer's decisions are used to compute a complex multi-dimensional score that is fed into
     the student's overall evaluation.
   \item A redesigned back end for our custom CMS for course materials, which our academic staff
     uses to author course syllabuses, lesson plans, assignments, etc.  In its prototype form,
     the application was built on Sinatra (Ruby) and MongoDB.  I rewrote it using Django and
     MySQL, built out additional functionality upon that foundation, and built a comprehensive
     suite of integration tests for it, as well as deployment scripts.
   \item In addition to application development, I carry substantial responsibilty for
     deployment and operation of all of our applications on AWS.
   \item Along with all of my colleagues, I'm directly involved in interviewing engineering
     candidates and making hiring decisions.
   \end{itemize}}

\headedsection
  {\textbf{Director of Engineering} at Learnist}
  {Feb 2012 -- Mar 2015}
  {\\Learnist was a social knowledge-sharing company that produced a website as well as mobile
    applications.  My major contributions included the following:
   \begin{itemize}
   \item Managed a team of 10--15 engineers at any given time, including mentoring the skills of
     junior engineers, facilitating technical discussions within the team, and making the final
     call on all hiring decisions.
   \item Served as the ultimate responsible individual for engineering issues as they affected
     people in other groups within the company.
   \item Personally oversaw all deployment and operation concerns in our AWS
     infrastructure. Authored a suite of user-friendly command-line tools for quickly and easily
     launching a new EC2 cluster with a copy of production data, scaling that cluster up or
     down, or terminating it.  This enabled members of my team to do extremely rapid and
     decentralized iteration on their features, as they could deploy their code at any time to a
     private sandbox environment that looked just like production, with just a few simple
     commands.
   \item Authored large parts of a Redis-backed cache for ActiveRecord objects that seamlessly
     handled concerns such as automatic lazy caching of objects and automatic cache
     invalidation.
   \item Personally implemented large swaths of back end code for the website:\ API controllers,
     business logic modules, ActiveRecord models, Resque jobs, etc.  Heavily optimized all of
     the above with the help of custom instrumentation and services like New Relic.
   \item Continually refactored code contributed by myself and others, discovering latent
     architectural patterns along the way, crystallizing those patterns into tight and cohesive
     interfaces, and sharing the learning with my team.
   \end{itemize}}

\headedsection
  {\textbf{Director of Engineering} at Grockit}
  {Jun 2008 -- Jan 2012}
  {\\Grockit produced an online environment to help students prepare for exams such as the SAT
    and GMAT in a fun and social game format.  The Grockit trademark and operations were sold to
    Kaplan in 2013, and it is still in operation today.  My major contributions included the
    following:
   \begin{itemize}
   \item Managed a team of 8-12 engineers, which entailed recruiting engineers, mentoring their
     skills, and facilitating group dynamics.
   \item Worked with our product team to define feature requirements, using the Agile
     Development method of expressing requirements in terms of ``user stories''.
   \item Managed our AWS infrastructure and the deployment of code thereto.
   \item Authored large amounts of code in the Rails 2.3 application that was our primary website.
   \item Contributed to our synchronous, multi-player game server, written in Java with
     Hibernate and Guice, and to its front-end code, which was written in a custom Javascript
     framework that did dynamic reactive rendering of HTML views, foreshadowing current
     technologies like Backbone and React.
   \end{itemize}}

\headedsection
  {\textbf{Software Engineer} at DataPower / IBM}
  {Apr 2000 -- Jun 2008}
  {\\I was the first employee at DataPower, which produced a line of network equipment for
    blazing-fast processing of XML Web Services protocols. From 2000 to 2005, the company grew
    from two people to nearly a hundred, and was eventually acquired by IBM. IBM continues to
    produce and market our products to this day.  Memorable contributions:
   \begin{itemize}
   \item A highly optimized XML parser built for reading and writing directly to network
     sockets. This was written in C using extreme optimization techniques to avoid ever polling
     the network, thus avoiding any blocking behavior.  Raw inline assembly code was used in
     certain key places to optimize the most critical operations.
   \item An optimizing compiler for the XSLT language. Interesting aspects of this project
     included an AST parser and optimizer (optimizations included constant folding, common
     subexpression elimination, and branch elimination), a single-static-assignment (SSA)
     intermediate representation supporting further optimizations (dataflow analysis, register
     allocation, etc.) and code generators for both x86 and SPARC targets.
   \end{itemize}}

\headedsection
  {\textbf{Software Engineer} at Art Technology Group (ATG)}
  {Sep 1998 -- Apr 2000}
  {\\ATG led the vanguard of companies doing e-commerce on the web in the late 90's. My role was
    initially to provide on-site support for customers, and later to implement some ancillary
    features, such as an adapter to connect our server application (ATG Dynamo) with a
    third-party CMS (Documentum).  All in all I was too green at the time to contribute much to
    the success of ATG, but this is where I learned a great deal about professional software
    development, including techniques like source control, automated testing, and release
    engineering, but more importantly, making a conscious commitment to enabling customer
    success.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\spacedhrule{0.8em}{-0.4em}

\roottitle{Skills}

\vspace{-1.0em}

\begin{multicols}{2}
\begin{itemize}
\item Python/Django/Celery (1 year)
\item Ruby/Rails/Resque (8 years)
\item Javascript (8 years) / Node.js (1 year)
\item SQL (15 years)
\item Redis (6 years)
\item AWS (EC2, S3, OpsWorks, SQS, etc.; 8 years)
\item Unix administration, shell scripting (20+ years)
\item Past experience:\ C, C++, Java, x86 assembler (12 years)
\item Test-Driven Development
\item Object-Oriented Domain Modeling
\item Process Automation
\item Continuous Integration / Continuous Delivery
\item ETL (Extract/Transform/Load) techniques
\item Recommendation Systems
\item Compiler Design and Implementation
\item Graph Algorithms
\end{itemize}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\spacedhrule{0.8em}{-0.4em}

\roottitle{Education}

\headedsection
  {Massachusetts Institute of Technology}
  {1994 -- 1998}
  {\\S.B., Electrical Engineering and Computer Science
   \\
   \\Areas of focus:
   \begin{itemize}
   \item Algorithms and Data Structures
   \item Parsers, Interpreters, and Compilers
   \item Recommendation Systems
\end{itemize}}

\end{document}
